Diffusive Nested Sampling: Not Dead Yet

### 2025-08-29 talk/talk.tex
Phase changes

>>>>

\begin{frame}
\frametitle{Thermodynamic Integration}
There are many methods based on the power posterior idea:

\begin{itemize}
\item Parallel tempering
\item Stepping-stone sampling
\item Sequential Monte Carlo
\item Simulated Tempering
\item More.
\end{itemize}

\begin{frame}
\frametitle{Power Posteriors: Problems}
There is a class of problems that defeats methods based on power posteriors.
These are {\bf phase change problems}. In statistical physics they are common,
but they also occur in Bayesian inference --- they involve a particular
shape to the likelihood function.

\begin{frame}
\frametitle{Phase Change Problems}

Let's explore how thermodynamic integration fails on phase change problems.
